---
title: "Text comparison"
author: "Xiaoxuan Liang"
date: "4/5/2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(tidytext)
library(janeaustenr)
library(stringr)
library(gutenbergr)
library(dplyr)
library(scales)
```

1.Pick three authors from Gutenberg.org and download their works.  
Compare the authors.  
Which two are more alike?  Some suggestions: Mark Twain, Leo Tolstoy, Charles Dickens. 
```{r}
#Three authors: Mark Twain, Leo Tolstoy, Charles Dickens
Mark <- c("Adventures of Huckleberry Finn","A Connecticut Yankee in King Arthur's Court")
Leo <- c("War and Peace","Anna Karenina")
Charles <- c("A Tale of Two Cities","Great Expectations")
Book_num <- function(book){
  ID <- vector("double",length(book))
  for(i in 1:length(book)){
    ID[i] <- gutenberg_works(title == book[i])
  }
  ID }
Book_num(Mark)
Book_num(Leo)
Book_num(Charles)

#Downloads
MarkD <- gutenberg_download(c(76,86))
LeoD <- gutenberg_download(c(2600,1399))
CharlesD <- gutenberg_download(c(98,1400))
```

```{r}
#Tidy
Tidy <- function(df){
  T_author <- df %>%
    unnest_tokens(word,text) %>%
    mutate(word= str_extract(word,"[a-z']+")) %>%
    anti_join(stop_words)
}
TMark <- Tidy(MarkD)
TLeo <- Tidy(LeoD)
TCharles <- Tidy(CharlesD)

```

```{r}
#Put all three authors together
frequency_authors <- bind_rows(mutate(TMark,author = "Mark"),
                              mutate(TLeo,author = "leo"),
                              mutate(TCharles,author = "Charles"))%>%
                      mutate(word = str_extract(word,"[a-z']+"))%>%
                      count(author,word)%>%
                      group_by(author)%>%
                      mutate(proportion = n/ sum(n))%>%
                      select(-n)%>%
                      spread(author,proportion)

 frequency_authors                         
```

```{r}
 #Frequencies
frequency1 <- frequency_authors %>%
   gather(author,proportion,`Mark`:`leo`)

frequency2 <- frequency_authors %>%
   gather(author,proportion,`leo`:`Charles`)

frequency1
frequency2
```

```{r}
#Grap the frequency comparison
#Charle vs LEO & Mark
ggplot(frequency1, aes(x = proportion,
        y = `Charles`,color = abs(`Charles` - proportion)))+
  geom_abline(color = "gray40", lty =2)+
  geom_jitter(alpha = 0.1,size= 2.5,
              width = 0.3,height = 0.3)+
  geom_text(aes(label= word),
            check_overlap = TRUE,vjust = 1.5)+
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  scale_color_gradient(limits = c(0, 0.001),
                        low = "darkslategray4",
                        high = "gray75") +
  facet_wrap(~author, ncol = 2) +
  theme(legend.position="none") +
  labs(y = "Charles", x = NULL)

#Mark vs Charls & Leo
ggplot(frequency2, aes(x = proportion,
        y = `Mark`,color = abs(`Mark` - proportion)))+
  geom_abline(color = "gray40", lty =2)+
  geom_jitter(alpha = 0.1,size= 2.5,
              width = 0.3,height = 0.3)+
  geom_text(aes(label= word),
            check_overlap = TRUE,vjust = 1.5)+
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  scale_color_gradient(limits = c(0, 0.001),
                        low = "darkslategray4",
                        high = "gray75") +
  facet_wrap(~author, ncol = 2) +
  theme(legend.position="none") +
  labs(y = "Mark", x = NULL)



```

```{r}
#Correlation1
df_Leo <- frequency1[frequency1$author == "leo",]
df_Mark <- frequency1[frequency1$author == "Mark",]
cor.test(data = df_Leo, ~ proportion + `Charles`)
cor.test(data = df_Mark, ~ proportion + `Charles`)

##Correlation1
df_Charles <- frequency2[frequency2$author == "Charles",]
df_leo <- frequency2[frequency2$author == "leo",]
cor.test(data = df_Charles, ~ proportion + `Mark`)
cor.test(data = df_leo, ~ proportion + `Mark`)

```
#From the grap and correlation table, Leo Tolstoy and Charles Dickens are more alike.





2.Let’s look at how the sentiment changes across the length of a book by looking at 80 lines at a time.  
Compare how sentiment changes in Victor Hugo’s Les Miserables and Charles Dickens’ A Tale of Two Cities.Look at negative vs positive sentiment.  
Then pick a sentiment like joy or anger or fear or …  and see how that sentiment compares.
{r}
victor <- gutenberg_download(c(135))
charles <- gutenberg_download(c(98))


tidy_victor <- victor %>% 
  mutate(volume= cumsum(str_detect(text, regex("^VOLUME (I|II|III|IV|V)")))) %>%
  mutate(volume= case_when(volume>0 ~ volume-1, volume==0 ~ 0)) %>%
  group_by(volume) %>%
  mutate(book= cumsum(str_detect(text, regex("^BOOK (First|Second|Third|Fourth|Fifth|Sixth|Seventh|Eight|Ninth|Tenth|Eleventh|Twelfth|Thirteenth|Fourteenth|Fifteenth)", ignore_case = TRUE)))) %>%
  group_by(volume, book) %>%
  mutate(linenumber = row_number(),chapter = cumsum(str_detect(text, regex("^chapter [\\divxlc]", ignore_case = TRUE)))) %>%
  ungroup() %>% 
  unnest_tokens(word, text) %>%
  select(volume, book, chapter, everything(),-gutenberg_id)



victor_sentiment <- tidy_victor %>%
  inner_join(get_sentiments("bing")) %>%
  count(volume, book, index = linenumber %/% 80, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)
  


# the sentiment analysis for all books in Volume 1 of Victor Hugo's Les Miserables
{r}

victor_sentiment %>% 
  filter(book!=0) %>%
  filter(volume == 1) %>%
  ggplot(aes(index, sentiment, fill= as.character(book))) +
  geom_col(show.legend = FALSE) + 
  facet_wrap(~book, ncol = 2, scales = "free_x")

#Volume 1 has 8 books. we can also look at volume 2.  


# have a look at positive vs negative sentiments for Victor:  
{r}
victor_counts <- tidy_victor %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

victor_counts %>% 
  group_by(sentiment) %>%
  top_n(10) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(y = "Contribution to sentiment (Victor)",
       x = NULL) +
  coord_flip()



{r}
tidy_charles <- charles %>% 
  mutate(book = cumsum(str_detect(text, regex("^Book the (First|Second|Third)", ignore_case = TRUE)))) %>%
  group_by(book) %>%
  mutate(linenumber = row_number(), chapter = cumsum(str_detect(text, regex("^(I|II|III|IV|V|VI|VII|VIII|IX|X|XI|XII|XIII|XIV|XV)\\.", ignore_case = TRUE)))) %>%
  ungroup() %>% 
  unnest_tokens(word, text) %>%
  select(book, chapter, everything(),-gutenberg_id) 
 


charles_sentiment <- tidy_charles %>%
  inner_join(get_sentiments("bing")) %>%
  count(book, index = linenumber %/% 80, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)
  



# the sentiment analysis for all books of Charles Dickensan's A Tale of Two Cities  

{r}
charles_sentiment %>%
  filter(book!=0) %>%
  ggplot(aes(index, sentiment, fill=as.character(book))) +
  geom_col(show.legend = FALSE) + 
  facet_wrap(~book, ncol = 2, scales = "free_x")
  
# more negative sentiments found in book 3  


#look at positive vs negative sentiments for Victor:  

{r}
charles_counts <- tidy_charles %>% 
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

charles_counts %>% 
  filter(word != "miss") %>% # Removed miss because it's mostly not a negative word
  group_by(sentiment) %>%
  top_n(10) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(y = "Contribution to sentiment (Charles)",
       x = NULL) +
  coord_flip()

  



{r}
nrcJoy <- get_sentiments("nrc") %>%
  filter(sentiment == "joy")


victorJoy <- tidy_victor %>%
  inner_join(nrcJoy) %>% 
  group_by(volume, book, chapter) %>%
  count()

victorJoy %>%
  filter(volume==1) %>% #####Only Looking at the books in first volume
  ggplot(aes(chapter, n)) +
  geom_line()+
  facet_wrap(~book, scales = "free_x")


charlesJoy <- tidy_charles %>% 
  inner_join(nrcJoy) %>% 
  group_by(book, chapter) %>%
  count()

charlesJoy %>% 
  filter(book!=0) %>% 
  ggplot(aes(chapter, n)) +
  geom_line()+
  facet_wrap(~book, scales = "free_x")
